A User-Extensible and Adaptable Parser Architecture

### 2008-08-22 doc/logparser-implementation.tex
Renamed MAIL_PICKED_FOR_DELIVERY to MAIL_QUEUED in thesis. Improved bibliography based on chktex suggestions.

    \item The indicator which more commonly introduces re-injection is when
        \daemon{qmgr} selects a mail with a previously unseen queueid for
        delivery (action: MAIL\_PICKED\_FOR\_DELIVERY\@; flowchart:~3), in
        which case a new data structure will be created for that mail.  The
        mail will be flagged as having unknown origins; this flag should be
        subsequently cleared once the origin has been established.  This
        may also be an indicator that the mail is a bounce notification,
        see \sectionref{identifying-bounce-notifications} for details.

@@

    \item [MAIL\_PICKED\_FOR\_DELIVERY] This action represents Postfix
        picking a mail from the queue to deliver. This action is used for
        both \daemon{qmgr} and \daemon{cleanup} as it needs to deal with
        out of order log lines; see \sectionref{discarding cleanup lines}
        for details.

@@

In the case where the \daemon{cleanup} line is still pending during the
TIMEOUT action the algorithm updates a global cache of queueids, adding the
queueid and the timestamp from the timeout line.  When the next
\daemon{cleanup} line is parsed for that queueid the cache will be checked
(during the MAIL\_PICKED\_FOR\_DELIVERY action),
and the line will be deemed part of the discarded mail and discarded if it
meets the following requirements:

>>>>

    \item The indicator which more commonly introduces re-injection is when
        \daemon{qmgr} selects a mail with a previously unseen queueid for
        delivery (action: MAIL\_QUEUED\@; flowchart:~3), in which case a
        new data structure will be created for that mail.  The mail will be
        flagged as having unknown origins; this flag should be subsequently
        cleared once the origin has been established.  This may also be an
        indicator that the mail is a bounce notification, see
        \sectionref{identifying-bounce-notifications} for details.

@@

    \item [MAIL\_QUEUED] This action represents Postfix
        picking a mail from the queue to deliver. This action is used for
        both \daemon{qmgr} and \daemon{cleanup} as it needs to deal with
        out of order log lines; see \sectionref{discarding cleanup lines}
        for details.

@@

In the case where the \daemon{cleanup} line is still pending during the
TIMEOUT action the algorithm updates a global cache of queueids, adding the
queueid and the timestamp from the timeout line.  When the next
\daemon{cleanup} line is parsed for that queueid the cache will be checked
(during the MAIL\_QUEUED action),
and the line will be deemed part of the discarded mail and discarded if it
meets the following requirements:
